---
title: "related Work"
author: "Ronald"
output: pdf_document
---

# Problem statement

As mentioned in section [**2**](# Related_work), there are benefits and limitations in specific psychosocial risk assessment methods, and in the technological approaches using sensors that support some assessments. The limitations related to the interruption of people's daily activities, in turn, entail an interpretation of cost and hindering of work in academic and labor fields. Furthermore, the intrusiveness associated with the use of electronic equipment for testing can provide data bias for testing. The latter corresponds to those cases in which the predisposition of people who are sometimes to electroencephalography, electromyography, or sensors aimed at measuring any skeletal muscle disorder is possible to the predisposition of the people evaluated. In addition to this, qualified personnel who are in charge of promoting the well-being and health of people do not have a detailed record of the risk factors that a particular person could be during the day.

According to these scenarios, a technological challenge can be seen, associated with data extraction, the cost attributed to the use of electronic equipment, and the bias implicit in them, corresponding to a technological challenge. In the works related in the section [**2.2**](#Related_work) and whose intervention was less intrusive, the focus was on facial recognition requiring close-up shots of the face. Additionally, although the evaluation was supported by measurement scales used in conventional evaluation methods, it can be seen that the extraction of information is strongly linked to the duration of the experimentation. Therefore, they lack continuous monitoring and can be recorded automatically. Another aspect of the problem that should be mentioned is the low number of works in which there is a conjunction between terms related to artificial intelligence and psychosocial risk assessment.

```{r related_terms, eval=T, echo=FALSE, message=F, warning=F}
library(dplyr)
library(kableExtra)
base_completa<-read.csv("../8_datasets_n_images/busqueda3.csv",sep =";",header=TRUE)
base_completa<-base_completa %>% mutate_if(is.numeric, format, digits=3,nsmall = 0)
base_completa<-base_completa[,c(1,2,3,18)]
kableExtra::kable(base_completa, caption="Keywords related to psycho-social affairs.",format='latex')%>%
      kable_styling(bootstrap_options = "striped", 
      font_size = 8,full_width = F,latex_options = "HOLD_position")
```

In the review carried out in the Web of Science browser, a date filter was applied to get articles published between 2000 and 2019. The quantities of search coincidences were extracted by using terms and keywords that are related to psychosocial risk factors. Additionally, the search for the above terms was executed by adding conjunction operators to terms and keywords related to artificial intelligence and machine learning. With the mentioned procedure, we expected to identify technological approaches where classification or regression tasks were defined to support psychosocial assessment.**Table \ref{tab:related_terms}**, shows the summary of amounts of work related to relevant topics in the context of them and their conjunction with terms related to AI. This evidence gives us an initial overview of technological contributions at the research level on issues that surrounds psychosocial risk factors. 

During the searching procedure, we add specific terms. A low number of works related to assessment can be seen in conjunction with terms related to artificial intelligence. A keywords selection, coding, and mapping were performed before the executions of queries. The selected terms were _artificial intelligence_, _computer vision_, _machine learning_, _neural network_, _deep learning_, _random forest_, _SVM_, _decision tree_, _linear regression_, _logistic regression_, _naive bayes_, _markov chain_, _fuzzy logic_, and _ensamble models_. Each term was coded in ascending numbering from 1 to 14, using the letter "T" as a prefix (see **Table \ref{tab:term_counts}**). Although there was evidences of works that address topics that surround our topic of interest, Their scope was oriented to specific aspects with little or no reference in its use within an interstate psycho-social assessment. 

```{r term_counts, eval=T, echo=FALSE, message=F, warning=F}
library(dplyr)
library(kableExtra)
base_completa<-read.csv("../8_datasets_n_images/busqueda3.csv",sep =";",header=TRUE)
base_completa<-base_completa %>% mutate_if(is.numeric, format, digits=3,nsmall = 0)
base_completa<-base_completa[,c(1,4:18)]
kableExtra::kable(base_completa, caption="Number of articles found with terms conjunction.",format='latex')%>%
      kable_styling(bootstrap_options = "striped", 
      font_size = 8,full_width = F,latex_options = "HOLD_position")
```

Given the prior statement, it is taking into account the lack of direct observation and the lack of automatic and intelligent follow-up and the intrusive limitations.  The following question was issued as a motivation for this project **_¿How to calculate indicators based on the detection of emotions and activities for monitoring and supporting the evaluation of psycho-social risk factors through automatic non-intrusive monitoring, using artificial intelligence techniques and computer vision?_**.

Based on the research question, the present work will focus on the extraction of activities and emotions that are related to quantifiable aspects within the psycho-social assessment. There are activities and emotions, implicit in the validation questionnaires. Data corresponding to daily activities in work and academic contexts could be a valuable source of information that can complement evaluations by providing metrics and indicators, or complementing the information that is currently acquired through the support systems previously seen. In the next section, the activities and emotions will be addressed and how the information inherent in them could constitute a contribution to the gap of artificial intelligence and its implication in the psycho-social assessment.
